Poster figures

### 2025-02-27 analysis/poster_ncar/presentation_figures.Rmd
CHanges size climatology
More figure tweaks

  breaks <- seq(-1, 1, by = 0.1)
  breaks <- breaks[breaks != 0]
  hindcast_clim |> 
    _[version == which_version] |>
    _[month_diff == which_lead] |> 
    # dcast(time + xgrid + ygrid ~ model, value.var = "aice") |> 
    # setnames(which_dataset, "obs") |>
    ggplot(aes(xgrid, ygrid)) +
    geom_contour_fill(aes(z = aice - obs, fill = after_stat(level)), 
                      breaks = breaks) +
    # geom_contour2(aes(z = aice - obs), breaks = AnchorBreaks(binwidth = 0.1, exclude = 0),
    #               linewidth = 0.1) +
    scale_fill_divergent_discretised(paste0(which_version, " bias at ", which_lead, " months at lead time"),
                                     low = trans_pink,
                                     high = trans_blue) +
    geomcoord_antarctica +
    geom_antarctica_fill +
    facet_wrap(~ month, 
               labeller = labeller(month = setNames(1:12, month.abb)),
               nrow = 2) +
    wide_legend +
    tag_facets()
}

@@

```{r}
width_errors <- 19.43/cm
height_errors <- 11.99/cm
```

@@

```{r fig-rmse_lon, fig.height=11.99/cm, fig.width=23.1/cm}
#| fig.cap: Meadian difference between RMSE of +S2 forecasts and persistence forecast at longitudinal bands.

>>>>

  breaks <- seq(-1, 1, by = 0.1)
  breaks <- breaks[breaks != 0]
  hindcast_clim |> 
    _[version == which_version] |>
    _[month_diff == which_lead] |> 
    # dcast(time + xgrid + ygrid ~ model, value.var = "aice") |> 
    # setnames(which_dataset, "obs") |>
    ggplot(aes(xgrid, ygrid)) +
    geom_contour_fill(aes(z = aice - obs, fill = after_stat(level)), 
                      breaks = breaks) +
    # geom_contour2(aes(z = aice - obs), breaks = AnchorBreaks(binwidth = 0.1, exclude = 0),
    #               linewidth = 0.1) +
    scale_fill_divergent_discretised(paste0(which_version, " bias at ", which_lead, " months at lead time"),
                                     low = trans_pink,
                                     high = trans_blue) +
    geomcoord_antarctica +
    geom_antarctica_fill +
    facet_wrap(~ month, 
               labeller = labeller(month = labels_month),
               nrow = 2) +
    wide_legend +
    tag_facets()
}

@@

```{r}
width_errors <- 23.87/cm
height_errors <- 11.99/cm
```

@@

```{r fig-rmse_lon, fig.height=12.6/cm, fig.width=23.1/cm}
#| fig.cap: Meadian difference between RMSE of +S2 forecasts and persistence forecast at longitudinal bands.
